The Driving Forces Behind API Evolution

### 2015-05-19 thesis/paper.tex
Disc draft

%Answer to RQ
Talk about the results regarding the law of familiarity that didn't apply.

@@

"1.1 Give a clear answer to the RQ. (Reject null / alternative)"

"1.2 Point to results"
%      -Bring up the most interesting/distinct trends

"1.3 Compare to literature (i.e. relate to previous work)"
 %      -Do our results agree with prev. work?

@@

\subsection{Contribution to Academia} 
Some laws don't apply. Consider inverting the law of org stab for APIs
Since motives are reverse engineerable, it hsould encourage more ppl to do similar studies

@@

\subsection{Contribution to Practice}
%       -How will our study help Axis? (More important)
The laws therefore form an environment within which the effectiveness of programming methodologies and management strategies and techniques can be evaluated, a backdrop against which better methodologies and techniques can be developed. [1980programs]

@@

       [quotes re. communication/stakeholders]:
       ``management must be thoroughly fami-liar with the organizational conventions and practices
involved, in order to make intelligent decisions.'' //Swanson
``provide a realistic and practical classification to facilitate communication about, and the
management of, software evolution and maintenance among researchers, practitioners, and their
managers;'' //Chapin

>>>>

1. 
       %Answer to RQ
       Functionality is the main driver for change, and it catalyses other changes

       %Point to results
       relate to enhanicve types
       relate to functuonality related laws

       %Relate to literature
       Refute refactorings paper
       Maybe something else

2. 
       %Answer to RQ
       Talk about the results regarding the law of familiarity that didn't apply.

@@

@@

\subsection{Implications for Academia} 
Reverse engineering/types: 
       Since we were able to correctly analyse which types they were, it should encourage academia to do more studies which reverse engineer theories etc.

Laws:
       Some laws don't apply. Consider inverting the law of org stab for APIs
       Since motives are reverse engineerable, it should encourage more ppl to do similar studies

@@

\subsection{Implications for Practitioners}
%       -How will our study help Axis? (More important)
The laws therefore form an environment within which the effectiveness of programming methodologies and management strategies and techniques can be evaluated, a backdrop against which better methodologies and techniques can be developed. [1980programs]

@@

       [quotes re. communication/stakeholders]:
       ``management must be thoroughly fami-liar with the organizational conventions and practices
       involved, in order to make intelligent decisions.'' //Swanson

       ``provide a realistic and practical classification to facilitate communication about, and the
       management of, software evolution and maintenance among researchers, practitioners, and their
       managers;'' //Chapin
